\section{Setup and procedure}
First we give an overview of the program which constitutes the experiment. In another subsection, 
we give a describtion of the setup used. 
\subsection{Procedure}
The procedure of measurements consists of the following six points:
\begin{enumerate}
    \item 
        \textbf{Assessing the detectors and probe at hand with the oscilloscope:}
        We measure the signals of the preamplifier (PA) as wel as uni- and bipolar outputs of 
        main amplifier (MA) at the oscilloscope. With this signal, we calculate the ascending time 
        of the signal.
    \item 
        \textbf{recording the energy spectrum of $^{57}$Co and $^{241}$Am:}
        The multichannel analyzer (MA) we measure the energy spectrum of both probes 
        for ca. 10 minutes. With the $^{57}$Co sample, we test the sensibility of each detector
        and the optimal positioning of the sample (which is not symmetric). After assigning the 
        channel-energy relationship based on the knowledge of some peaks, we interprete the other visible peaks.
    \item
        \textbf{setting the energy windows:}
        In this step, we restrict the events passed by the single channel analyzer (SCA) to those 
        of the 14.4 keV and 122 keV photons, respectively.
    \item
        \textbf{measuring the delayed coincidences:}
        Using the Time-to-Amplitude converter (TAC), we record the delays between 14.4 keV and 122 keV 
        events. Since the 14.4 keV photon is only emitted in 10 \% of the cases, we use this signal to start the 
        TAC, and stop with the delayed 122 keV photon, expecting to drastically reduce the dead time of the 
        measurement.
    \item
        \textbf{measuring the background (random coincidences):}
        Taking out the delay of the 122 keV signal and further introducing a delay on the 14.4 keV signal, 
        we measure the background. 
    \item
        \textbf{time calibration of Time to Amplitude converter (TAC):}
        In order to correlate measured channel and the respective time delay, we 
\end{enumerate}







\subsection{Experimental setup}


